Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-10 proposal/proposal.tex
Added pretty figures and text

\section{Proposed Work}
\subsection{Overview}
The project we are proposing will be an extension of the ACMx SmartLots project. We will collaborate closely with the ACMx group to create and deploy the first working parking lot monitoring system on the Mines campus. Our system will consist of several subsystems, each of which will be either an extension of a current ACMx subsystem or a new subsystem that will interface with the ACMx architecture. Figure 1 shows the overall architecture of our system, overlaid on a non-scaled map of the CTLM parking lots.

% Insert Image here. Is it OK for me to refer to it as 'figure 1' or should I change that part? Thanks for creating this graphic Santi!

@@

\subsection{Server Processing}
Once an image has been determined to contain a license plate, it will be transmitted from the Acquisition Raspberry Pi to a server online via the Central Basestation Pi. The server will then be responsible for using recognition software technology to extract the digits of the license plate from the image. Upon successful completion, the textual representation of the license plate will be stored in a database residing on the server to be later integrated into a front-facing web application.

The subsystem encapsulating server processing will require a review of recognition software and literature. There exists a market for Automatic License Plate Recognition (ALPR) software that relies on Optical Character Recognition (OCR) engines to extract characters. \cite{du2013} describes the various methods and features used to extract characters from a license plate. Once an ALPR solution is chosen, it will be necessary to collect a set of test data using the Acquisition Pi to tune the workflow of character extraction. Because the system is being deployed in the Denver metro area, it can be assumed that Colorado plates will make up the majority of license plates the system will detect.

@@

Collection of test data would require using the Acquisition Pi to take images, as this would simulate the real-world use of the application.

@@

\subsubsection{Interface with Basestation Pi}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Pi that takes the images of cars. Instead, it is assumed all communications will come through the Basestation Pi, and that the Basestation Pi will upload received images to the ACMx Linux server (See section 2.6.1 about the HTTP interface).

Upon upload of the image to the ACMx server, a script will be invoked to process the image. The ACMx server will then run redundancy measures to ensure the image uploaded does contain a license plate. Upon a successful identification, the server will invoke the selected ALPR strategy to extract characters from the license plate image. Cropping and image manipulation required by the selected ALPR strategy will be done before invoking this script. The amount of cropping done on the server and on the Acquisition Pi is something to be determined throughout the course of this project. Section 2.3 goes into more detail about this subject.

@@

\subsubsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, as mentioned in section 2.4, we will be collecting periodic overhead images from a camera mounted on the base station Raspberry Pi. These images will serve as a visual representation of how many cars are actually in the parking lot at the time the image was taken. Administrators should be able to periodically compare this image to the collected data from the sensor network to make sure the numbers being computed by the network accurately represent the number of cars in the lot. As previously mentioned, the deployment of this project will only be on two campus parking lots, and we may only have one overhead camera to start off with, although ideally we would have two - one for each lot. The web interface will allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator should be able to overwrite the count in the database to reflect reality. This interface will be extremely useful in helping us to calibrate the system. For example, if the sensors are consistently reporting less cars in the lot than the image shows, we can fine-tune the collection process to make sure fewer cars slip through unnoticed. Future work in this area will include an automated version of this process, where a computer program will compare the image to the sensed data and make any necessary corrections.

@@

\subsection{Deployment}
Blah

>>>>

\section{Proposed Work}
\subsection{Overview}
The project we are proposing will be an extension of the ACMx SmartLots project. We will collaborate closely with the ACMx group to create and deploy the first working parking lot monitoring system on the Mines campus. Our system will consist of several subsystems, each of which will be either an extension of a current ACMx subsystem or a new subsystem that will interface with the ACMx architecture. Figure \ref{fig:system} shows the overall architecture of our system, overlaid upon a non-scaled map of the CTLM parking lots.

\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{architecture}
\end{center}
\caption{Overall System Architecture}
\label{fig:system}
\end{figure}

@@

\subsection{Server Processing}
Once an image has been determined to contain a license plate, it will be transmitted from the Acquisition Raspberry Pi to a server online via the Central Basestation Raspberry Pi. The server will then be responsible for using recognition software technology to extract the digits of the license plate from the image. Upon successful completion, the textual representation of the license plate will be stored in a database residing on the server to be later integrated into a front-facing web application.

The subsystem encapsulating server processing will require a review of recognition software and literature. There exists a market for Automatic License Plate Recognition (ALPR) software that relies on Optical Character Recognition (OCR) engines to extract characters. \cite{du2013} describes the various methods and features used to extract characters from a license plate. Once an ALPR solution is chosen, it will be necessary to collect a set of test data using the Acquisition Raspberry Pi to tune the workflow of character extraction. Because the system is being deployed in the Denver metro area, it can be assumed that Colorado plates will make up the majority of license plates the system will detect.

@@

Collection of test data would require using the Acquisition Raspberry Pi to take images, as this would simulate the real-world use of the application.

@@

\subsubsection{Interface with Basestation Raspberry Pi}
The recognition and extraction of license plate characters will not directly interface with the Arduino Fio or Acquisition Raspberry Pi that takes the images of cars. Instead, it is assumed all communications will come through the Basestation Raspberry Pi, and that the Basestation Raspberry Pi will upload received images to the ACMx Linux server (See section 2.6.1 about the HTTP interface).

Upon upload of the image to the ACMx server, a script will be invoked to process the image. The ACMx server will then run redundancy measures to ensure the image uploaded does contain a license plate. Upon a successful identification, the server will invoke the selected ALPR strategy to extract characters from the license plate image. Cropping and image manipulation required by the selected ALPR strategy will be done before invoking this script. The amount of cropping done on the server and on the Acquisition Raspberry Pi is something to be determined throughout the course of this project. Section 2.3 goes into more detail about this subject.

@@

\subsubsection{Validating and Adjusting Lot Capacity Data}
We expect that our first deployment of this system may not be 100\% accurate at detecting all vehicles that enter and exit lots. Therefore, as mentioned in section 2.4, we will be collecting periodic overhead images from a camera mounted on the base station Raspberry Pi. These images will serve as a visual representation of how many cars are actually in the parking lot at the time the image was taken. Administrators should be able to periodically compare this image to the collected data from the sensor network to make sure the numbers being computed by the network accurately represent the number of cars in the lot. As previously mentioned, the deployment of this project will only be on two campus parking lots, and we may only have one overhead camera to start off with, although ideally we would have two - one for each lot. The web interface will allow administrators to pull up the image for any lot with an overhead camera and see the numbers for that lot right next to the image. If any discrepancies are found, the administrator should be able to overwrite the count in the database to reflect reality. This interface will be extremely useful in helping to calibrate the system. For example, if the sensors are consistently reporting less cars in the lot than the image shows, we can fine-tune the collection process to make sure fewer cars slip through unnoticed. Future work in this area will include an automated version of this process, where a computer program will compare the image to the sensed data and make any necessary corrections.

@@

\subsection{Deployment}
The system is planned to be deployed at the CTLM Upper and Lower parking lots at the Colorado School of Mines. These parking lots were chosen because of their accessible location, unobstructed visibility from a campus structure, and wide use. Both parking lots have two entryways, each of which will be equipped with an automobile detection subsystem as shown in Figure \ref{fig:deployment}. All entryways also benefit from having a clear view of the sky for increased photovoltaic efficiency.

\begin{figure}
\begin{center}
\includegraphics[width=5in]{deployment}
\end{center}
\caption{Deployment Location}
\label{fig:deployment}
\end{figure}

The central basestation, as described in Section 2.4, will be located on the second level of the CTLM building. Several potential locations exist which allow for a clear line-of-sight to all automobile detection subsystems, one of which is detailed in Figure \ref{fig:deployment}. These locations also provide internet access to the Central Basestation Raspberry Pi through ethernet ports.
